OwO

### 2020-02-20 msc_english_contents.tex
EfficientNet start

\section{Scope of study}

\section{Structure of thesis}
Cool stuff etc.

\chapter{Neural networks}
Background stuff 
\section{Fully Connected Networks}
When needed example of a transfer learning head?, when good/bad
\section{Convolutional Neural Networks}
Show some basic CNN things maybe and why needed over fully connected bois :) 
\subsection{Neural image processing}
How it different from classical features and how/why it works
\section{Attention}
Attention huh
\section{Multi-task learning}
Describe how a multi-task setting differs or maybe in the other chapter only?
\section{RNN/LSTM/Transformer text processing/generation}
Depending on what may be used

@@

\section{ResNet}
ResNet is one of the first effective and very deep Convolutional Neural Network architecture that was presented in 2015 and won the ImageNet challenge. Prior to the publication of ResNet, the most powerful networks were relatively shallow, like VGGNet, which has only 19 layers. One of the big issues relating to deep networks is vanishing gradients, where gradients disappear when they are backpropagated through many layers. ResNets utilize residual connections around bottleneck building blocks, which allow for the networks to contain many more layers than those without them, the largest network presented in the original ResNet paper was 152 layers, totaling for around 8x increase in the number of layers when compared to earlier networks \citep{resNet}.

@@

The ResNet block architecture allows for the blocks to learn the identity function more efficiently by trying to learn the residual function instead of the direct mapping. Normally a mapping is learned between ${x}$ and ${y}$ using a function ${H(x)}$ but by the same token, we can learn a residual transformation, ${F(x) = H(x) - x}$, where ${H}$ is the mapping of two or more network layers. Both of these approaches should approximate the same functions; the difference is in how easy it is for the network to learn. Learning a transformation of ${F(x) = 0}$ would intuitively seem easier for a neural network than learning ${F(x) = x}$. As can be seen from the success of the ResNets, this is what allows for creating very deep networks. If the transformation changes the input size, a matrix ${W}$ is necessary to map the input to the same dimensions, generating the final formula for a residual block ${y = F(x, \{W_i\}) + W_s x}$.

Many variants of ResNet exists, such as wide ResNets \citep{wideResNet}, ResNeXt \citep{resNext} and others. Also the DenseNet \citep{denseNet} is heavily inspired by ResNets. ResNet is still one of the most popular backbones to use when an ImageNet trained backbone is needed for some part of a classifier.

\chapter{Object detection}
Based on what is going to be detected, maybe text, cars, people?
\chapter{Paragraph captioning}
Assuming we are doing this
\chapter{Multi task learning}
Cover some examples of MTL in Computer Vision, differences to Transfer Learning, why it might work, why we might see detrimental results and why it might be beneficial (results/performance)

\chapter{Datasets}
Describing our data
\section{Data formats}
Describe what datasets are used for each of the tasks and where they are from etc.

>>>>

Multi-task learning proposes some solutions to these problems but makes the training process more difficult. Still, in some cases, it is something that has to be done to get a good enough inference time and accuracy on the problem at hand. Many modern computer vision models already feature an ImageNet backbone as a part of the classifier, so this is a good part of the network to consider for sharing, but finding which tasks and how much can be shared is a difficult problem to solve.

\section{Scope of study}
In this thesis, we will study state-of-the-art solutions to some computer vision problems, like image classification, object detection, and text recognition. Then we will train classifiers that solve these problems using various data sets and try to combine them to produce a single multi-task network using multi-task learning. We will then evaluate how easy and effective it is to share the weights within similar and different tasks.
\chapter{Neural networks}
Background stuff 
\section{Fully Connected Networks}
When needed example of a transfer learning head?, when good/bad
\section{Convolutional Neural Networks}
Show some basic CNN things maybe and why needed over fully connected bois :) 
\subsection{Neural image processing}
How it different from classical features and how/why it works
\section{Attention}
Attention huh
\section{Multi-task learning}
Describe how a multi-task setting differs or maybe in the other chapter only?
\section{RNN}
Depending on what may be used

@@

\section{ResNet}
ResNet is one of the first effective and very deep Convolutional Neural Network architecture that was presented in 2015 and won the ImageNet challenge. Prior to the publication of ResNet, the most powerful networks were relatively shallow, like VGGNet, which has only 19 layers. One of the big issues relating to training deep networks is vanishing gradients, where gradients disappear when they are backpropagated through many layers \citep{wideResNet}. ResNets utilize residual connections around bottleneck building blocks, which allow for the networks to contain many more layers than those without them, the largest network presented in the original ResNet paper was 152 layers, totaling for around 8x increase in the number of layers when compared to earlier networks \citep{resNet}.

@@

The ResNet block architecture allows for the blocks to learn the identity function more efficiently by trying to learn the residual function instead of the direct mapping. Normally a mapping is learned between ${x}$ and ${y}$ using a function ${H(x)}$ but by the same token, we can learn a residual transformation, ${F(x) = H(x) - x}$, where ${H}$ is the mapping of two or more network layers. Both of these approaches should approximate the same functions; the difference is in how easy it is for the network to learn. Learning a transformation of ${F(x) = 0}$ would intuitively seem easier for a neural network than learning ${F(x) = x}$. As can be seen from the success of the ResNets compared to non-residual networks, this is what allows for creating very deep networks. If the transformation changes the input size, a matrix ${W}$ is necessary to map the input to the same dimensions, generating the final formula for a residual block ${y = F(x, \{W_i\}) + W_s x}$.

Many variants of ResNet exists, such as wide ResNets \citep{wideResNet}, ResNeXt \citep{resNext} and others. Also the DenseNet \citep{denseNet} is heavily inspired by ResNets. ResNet50, ResNet34, ResNet101, and ResNet152 are still some of the most popular models to use when an ImageNet trained backbone is needed for some part of a classifier as they produce good results and do not contain too many parameters compared to some other architectures.

\section{Improving model performance}
Go through depth, width, resolution, some neural architecture search

\section{EfficientNet}
EfficientNet models form a family of models ranging from EfficientNet0 to EfficientNet7 that were generated by smartly scaling existing convolutional models to optimize them for efficiency \citep{efficientNet}. The more complex models are created by using compound scaling on the EfficientNet0 model, where the width, depth, and the resolution of the network are scaled using a factor ${\phi}$. The search of ${\phi}$ is an optimization problem, where the goal is to optimize for both accuracy and number of floating-point operations. This search is only done on the base model because the neural architecture search used to find the parameter becomes very expensive as the model size increases \citep{efficientNet}.

The proposed EfficientNet models use mobile inverted bottleneck (MBConv) blocks used in MobileNetV2 \citep{mobileNetv2} in constructing the base model. The MobileNet uses a Depthwise Separable Convolution, where a depthwise convolution and a pointwise convolution are applied in sequence. The depthwise convolution applies ${d_i}$ ${k x k}$ filters to the input, where ${d_i}$ is the input channels and ${k}$ is the kernel size leading to an output channel count ${d_j = d_i}$. A normal convolutional layer would apply multiple filters having ${M}$ channels with the computational cost of ${h_i w_i d_i d_j k^2}$, whereas the depthwise convolution only has a cost of ${h_i w_i d_i (k^2 + d_j)}$, reducing the cost by ${k^2}$. The result of the depthwise convolution then runs through a pointwise convolution, where a 1 x 1 x ${d_j}$ 1d convolution is applied to get the final output as a linear combination of the channels.

\chapter{Object detection}
Based on what is going to be detected, maybe text, cars, people?
\chapter{Paragraph captioning}
Assuming we are doing this
\chapter{Multi task learning}
Cover some examples of MTL in Computer Vision, differences to Transfer Learning, why it might work, why we might see detrimental results and why it might be beneficial (results/performance)
\section{Definition}
\section{Benefits}
\section{Hard parameter sharing}
\section{Soft parameter sharing}
\section{Special multi-task approaches}
\section{Multi-task learning with little data}
\section{What and when to share}
\section{Succesful multi-task learning applications}
\chapter{Datasets}
Describing our data
\section{Data formats}
Describe what datasets are used for each of the tasks and where they are from etc.
